---
title: "EasternCanadaClassifier Module"
date: "`r Sys.Date()`"
output:
html_document:
toc: true
toc_float: true
theme: sandstone
number_sections: true
---

# Overview

This report demonstrates the **EasternCanadaClassifier** module applied to multiple jurisdictions:

* Newfoundland & Labrador (NL)
* Alberta (AB)

The classifier assigns forest stands to **Analysis Units (AUs)** using:

* species composition
* stand age
* yield curves

---

# Setup

```{r setup, message=FALSE, warning=FALSE}
library(SpaDES.core)
library(SpaDES.project)
library(terra)
library(data.table)

setPaths(
  modulePath = "modules",
  inputPath  = "data",
  outputPath = "outputs",
  cachePath  = "cache"
)
```

---

# Load Yield Files

```{r}
yieldFiles_NL <- list.files("data/NL", pattern = "\\.yld$", full.names = TRUE)
yieldFiles_AB <- list.files("data/AB", pattern = "\\.csv$", full.names = TRUE)

yieldFiles <- c(yieldFiles_NL, yieldFiles_AB)

length(yieldFiles_NL)
length(yieldFiles_AB)
```

---

# Run Simulation

```{r}
sim <- simInit(
  times   = list(start = 0, end = 1),
  modules = "EasternCanadaClassifier",
  params = list(
    EasternCanadaClassifier = list(
      yieldFiles = yieldFiles
    )
  )
)

sim <- spades(sim)
```

---

# Overall Results

```{r}
table(sim$analysisUnitDT$bestCurve)
```

---

# Newfoundland (NL)

## Filter NL pixels

```{r}
nl_data <- sim$analysisUnitDT[grepl("NPen|Central|West|Bar", bestCurve)]
```

## Distribution

```{r}
table(nl_data$bestCurve)
```

## Map

```{r}
terra::plot(sim$analysisUnitMap, main = "NL Analysis Units")
```

---

# Alberta (AB)

## Filter AB pixels

```{r}
ab_data <- sim$analysisUnitDT[!grepl("NPen|Central|West|Bar", bestCurve)]
```

## Distribution

```{r}
table(ab_data$bestCurve)
```

## Map

```{r}
terra::plot(sim$analysisUnitMap, main = "AB Analysis Units")
```

---

# Comparison

```{r}
nl_counts <- table(nl_data$bestCurve)
ab_counts <- table(ab_data$bestCurve)

nl_counts
ab_counts
```

---

# Interpretation

* NL classification is driven by **YLD curves**
* AB classification uses **yield tables**
* Regional filtering improves ecological realism
* Curve dominance reflects landscape composition

---

# Notes

* Current implementation uses **region-aware filtering**
* Province-specific logic is maintained internally
* The framework is extensible to additional provinces

---

# Next Steps

* Automate region-to-curve mapping
* Add province-specific validation
* Integrate with AAC module

---
