---
title: "EasternCanadaClassifier Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'EasternCanadaClassifier', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
bibliography: citations/references_EasternCanadaClassifier.bib
link-citations: true
always_allow_html: true
---

# EasternCanadaClassifier Module

(ref:EasternCanadaClassifier) *EasternCanadaClassifier*

```{r setup-EasternCanadaClassifier, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold")

```
Authors

r paste(as.character(SpaDES.core::moduleMetadata(module = "EasternCanadaClassifier", path = '..')$authors), sep = ', ')

Module Overview
Module summary

The EasternCanadaClassifier module classifies forest stands into Analysis Units (AUs) using information from the forest simulation state.

Analysis Units represent groups of stands with similar growth trajectories and are used to link the landscape to yield tables for forest harvest planning and AAC (Annual Allowable Cut) calculations.

The classifier operates on the LandR forest state, using:

stand biomass

species composition

stand age

pixel grouping

The module assigns each spatial pixel group to the most appropriate yield curve.

The output is a raster called analysisUnitMap which identifies the analysis unit associated with each forest pixel.

Module inputs and parameters

This module expects inputs generated by upstream modules in the simulation pipeline.

Typical upstream modules include:

EasternCanadaDataPrep

RiparianBuffers

EasternCanadaLandbase

LandR forest dynamics modules

If these inputs are not available, the module can generate synthetic placeholder inputs for standalone testing.

Table @ref(tab:moduleInputs-EasternCanadaClassifier) shows the full list of module inputs.


```{r df_inputs <- SpaDES.core::moduleInputs("EasternCanadaClassifier", "E:/EasternCanadaClassifier")
knitr::kable(df_inputs,
             caption = "List of (ref:EasternCanadaClassifier) input objects and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)